Modelling the emergence of whisker barrels

### 2020-07-03 paper/briefpaper/brief.tex
Move a mis-placed paragraph
Move this short para agin, this time to the start of Materials and Methods

@@

% for ``end of methods''
\MPone{We concentrated on the representation of the forty-six macrovibrissae
  that constitute a given barrel field, because their thalamic and cortical
  correlates are easily identifiable and consistently positioned. We exclude
  the representation of the microvibrissae to limit the overall complexity of
  the simulations, as well as the five rhinal whiskers as their representation
  in S1 is isolated from the main barrel field. Consequently, we set $N=41$.}

>>>>

\MPone{We concentrated our simulation work on the representation of the
  forty-six macrovibrissae that constitute a given barrel field, because their
  thalamic and cortical correlates are easily identifiable and consistently
  positioned. We excluded the representation of the microvibrissae to limit
  the overall complexity of the simulations, as well as the five rhinal
  whiskers as their representation in S1 is isolated from the main barrel
  field. Consequently, we set $N=41$.}

@@
